Pyg4ometry : A Tool to Create Geometries for Geant4, BDSIM, G4Beamline and FLUKA for Particle Loss and Energy Deposit Studies

### 2019-05-19 public/2019-ipac/WEPTS054.tex
Updated doc strings for manual

\section{EXAMPLES}
\subsection{Python}
A complete code example for creation of a simple geometry consisting of three Iron solids is shown below. The python interfaces are so similar to the Geant4 C++ interface and the user can refer to the Geant4 documentation.  
\VerbatimInput[fontsize=\small]{./examples/simple.py}
The code is divided in 6 blocks of definitions, reusable parameters, materials, solids, structure and placement, GDML IO and finally visualisation. A key difference between \verb|pyg4ometry| and Geant4 is a dedicated object known as the \verb|Registry| to store all geometry definitions to be stored in the output file. The VTK output from this example is shown in Figure~\ref{fig:simple}, where three solids, a cube, sphere and cylinder, are placed with translations and rotations within a cubical world volume.
\begin{figure}[!htb]
   \centering
   \includegraphics*[width=.9\columnwidth]{./examples/simple.jpg}
   \caption{Example of three primitive Geant4 solids rendered in VTK.}
   \label{fig:simple}
\end{figure}

Figure \ref{fig:dipole} shows a more complex geometry example of a cavity beam position monitor and short sections of beam pipe.
\begin{figure}[!htb]
   \centering
   \includegraphics*[width=.8\columnwidth]{./examples/dipole.jpg}
   \caption{Example of a more complex geometry example, a cavity beam position monitor.}
   \label{fig:dipole}
\end{figure}

\subsection{Standard tessellation language (STL)}
STL file format describes a raw unstructured triangulated surface, where the surface normal is defined by the ordering of the vertices. \verb|Pyg4ometry| supports the loading 
STL files and conversion to G4TessellatedSolid. A classic STL example loaded in \verb|pg4ometry| and displayed in VTK is shown in Figure~\ref{fig:utahteapot}
\VerbatimInput[fontsize=\small]{./examples/stl.py}
\begin{figure}[!htb]
   \centering
   \includegraphics*[width=.6\columnwidth]{./examples/utahteapot.jpg}
   \caption{STL surface mesh rendered in VTK using pyg4ometry.}
   \label{fig:utahteapot}
\end{figure}

\subsection{Computer aided design/manufacturing (CAD/CAM)}
Arbitrary conversion of CAD/CAM files to \verb|pyg4ometry| is a very challenging task. Typically users convert the CAD description into
an intermediate surface triangulation format (such as STL described previously) and load the geometry as a G4TessellatedSolid. An interface for
loading STEP/STP files was creating using FreeCAD/OpenCASCADE. A single solid in general corresponds to a {\it part} and multiple placements 
of a solid to a {\it part assembly}.
A example of a conversion of a large STEP file to pyg4ometry/GDML is shown in Figure~\ref{fig:ea910}.
\VerbatimInput[fontsize=\small]{./examples/freecad.py}
\begin{figure}[!htb]
   \centering
   \includegraphics*[width=1.0\columnwidth]{./examples/ea9-10.jpg}
   \caption{Example a conversion from STEP file description of the shielding of the CERN East Area T8 and T11 test beam lines to GDML. Each part is 
   given a randomly assigned colour to clearly indicate the structure of the shielding.}
   \label{fig:ea910}
\end{figure}

\section{BDSIM}
Geometry created by \verb|pyg4ometry| can be directly loaded into Geant4 based. Figure~\ref{fig:dipole-bdsim} shows the cavity BPM 
example loaded into BDSIM. 
\begin{figure}[h!tb]
   \centering
   \includegraphics*[width=1.0\columnwidth]{./examples/dipole_bdsim.jpg}
   \caption{Example of geometry in Geant4/BDSIM. The example shows a 50~GeV proton interacting with the geometry material.}
   \label{fig:dipole-bdsim}
\end{figure}

>>>>

\section{EXAMPLES}
\subsection{Python}
A complete code example for creation of a simple geometry consisting of three Iron solids is shown below. The python interfaces are so similar to the Geant4 C++ interface and the user can refer to the Geant4 documentation.  
%\VerbatimInput[fontsize=\small]{./examples/simple.py}
\VerbatimInput[fontsize=\small]{simple.py}
The code is divided in 6 blocks of definitions, reusable parameters, materials, solids, structure and placement, GDML IO and finally visualisation. A key difference between \verb|pyg4ometry| and Geant4 is a dedicated object known as the \verb|Registry| to store all geometry definitions to be stored in the output file. The VTK output from this example is shown in Figure~\ref{fig:simple}, where three solids, a cube, sphere and cylinder, are placed with translations and rotations within a cubical world volume.
\begin{figure}[!htb]
   \centering
   %\includegraphics*[width=.9\columnwidth]{./examples/simple.jpg}
   \includegraphics*[width=.9\columnwidth]{simple.jpg}
   \caption{Example of three primitive Geant4 solids rendered in VTK.}
   \label{fig:simple}
\end{figure}

Figure \ref{fig:dipole} shows a more complex geometry example of a cavity beam position monitor and short sections of beam pipe.
\begin{figure}[!htb]
   \centering
   %\includegraphics*[width=.8\columnwidth]{./examples/dipole.jpg}
   \includegraphics*[width=.8\columnwidth]{dipole.jpg}
   \caption{Example of a more complex geometry example, a cavity beam position monitor.}
   \label{fig:dipole}
\end{figure}

\subsection{Standard tessellation language (STL)}
STL file format describes a raw unstructured triangulated surface, where the surface normal is defined by the ordering of the vertices. \verb|Pyg4ometry| supports the loading 
STL files and conversion to G4TessellatedSolid. A classic STL example loaded in \verb|pg4ometry| and displayed in VTK is shown in Figure~\ref{fig:utahteapot}
%\VerbatimInput[fontsize=\small]{./examples/stl.py}
\VerbatimInput[fontsize=\small]{stl.py}
\begin{figure}[!htb]
   \centering
   %\includegraphics*[width=.6\columnwidth]{./examples/utahteapot.jpg}
   \includegraphics*[width=.6\columnwidth]{utahteapot.jpg}

   \caption{STL surface mesh rendered in VTK using pyg4ometry.}
   \label{fig:utahteapot}
\end{figure}

\subsection{Computer aided design/manufacturing (CAD/CAM)}
Arbitrary conversion of CAD/CAM files to \verb|pyg4ometry| is a very challenging task. Typically users convert the CAD description into
an intermediate surface triangulation format (such as STL described previously) and load the geometry as a G4TessellatedSolid. An interface for
loading STEP/STP files was creating using FreeCAD/OpenCASCADE. A single solid in general corresponds to a {\it part} and multiple placements 
of a solid to a {\it part assembly}.
A example of a conversion of a large STEP file to pyg4ometry/GDML is shown in Figure~\ref{fig:ea910}.
%\VerbatimInput[fontsize=\small]{./examples/freecad.py}
\VerbatimInput[fontsize=\small]{freecad.py}
\begin{figure}[!htb]
   \centering
   %\includegraphics*[width=1.0\columnwidth]{./examples/ea9-10.jpg}
   \includegraphics*[width=1.0\columnwidth]{ea9-10.jpg}
   \caption{Example a conversion from STEP file description of the shielding of the CERN East Area T8 and T11 test beam lines to GDML. Each part is 
   given a randomly assigned colour to clearly indicate the structure of the shielding.}
   \label{fig:ea910}
\end{figure}

\section{BDSIM}
Geometry created by \verb|pyg4ometry| can be directly loaded into Geant4 based. Figure~\ref{fig:dipole-bdsim} shows the cavity BPM 
example loaded into BDSIM. 
\begin{figure}[h!tb]
   \centering
   %\includegraphics*[width=1.0\columnwidth]{./examples/dipole_bdsim.jpg}
   \includegraphics*[width=1.0\columnwidth]{dipole_bdsim.jpg}
   \caption{Example of geometry in Geant4/BDSIM. The example shows a 50~GeV proton interacting with the geometry material.}
   \label{fig:dipole-bdsim}
\end{figure}
